---
title: "Pricing Investigation"
author: "Jason Richardson"
date: "8/13/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(data.table)
library(tidyverse)
library(knitr)

order.info <- fread("data/bogdandata/SO_RacetracAndOthers_2017_20190729_dates.csv")

order.info <- order.info %>% 
  filter(`Primary GroupDesc` == "7-ELEVEN" |
         `Primary GroupDesc` == "RACETRAC PETROLEUM" |
         `Primary GroupDesc` == "SPEEDWAY") %>% 
  mutate(max.qty = pmax(`Ordered Qty`, `Delivered Qty`)) %>% 
  rename(MaterialNo = `Material No`,
         sold.to = `Sold To`) %>% 
  mutate(OrderDate = as.Date(as.character(OrderDate), "%Y%m%d"))

products.price <- fread("data/bogdandata/Products_Price.csv")

products.price <- products.price %>% 
  filter(KeyAccount == "7-ELEVEN" |
         KeyAccount == "RACETRAC PETROLEUM" |
         KeyAccount == "SPEEDWAY")

products.price$Price_RC <- round(products.price$Price_RC, 2)
```

## Is there a variation in unit price from customer to customer?

Short answer: yes. 

Using the products price csv, pulling 20 random products, we see different price across Key Accounts when dividing volume by DNR.

```{r unit.price, echo = FALSE}
# get random sample of 20 products

samp.prod <- products.price %>% 
  select(MaterialNo) %>% 
  unique() %>% 
  sample_n(15)

print.data.frame(products.price %>% 
  semi_join(samp.prod, "MaterialNo") %>% 
  select(-c(Volume, DNR)) %>%
  select(Product, KeyAccount, Price_RC) %>% 
  mutate(KeyAccount = recode(KeyAccount, "RACETRAC PETROLEUM" = "RACETRAC")) %>% 
  arrange(Product))

```

## Is there a variation in unit price over time?

Maybe. There are relatively flat lines for each outlet but what are the spikes? Are those net values accidentally making their way in?

```{r netvalue.time, echo=FALSE}
one.samp.prod <- products.price %>% 
  select(MaterialNo) %>% 
  unique() %>% 
  # sample_n(1)
  filter(MaterialNo == 115583) #115583 is good if don't want to use random, 12 pack Coke

ten.samp.stores <- order.info %>% 
  select(sold.to) %>% 
  unique() %>% 
  sample_n(10)

order.random <- order.info %>% 
  semi_join(one.samp.prod, "MaterialNo") %>% 
  semi_join(ten.samp.stores, "sold.to")

order.random %>% 
  ggplot(aes(y = NetPrice, x = OrderDate, color = as.factor(sold.to))) +
  geom_line(position=position_jitter(h = 0.2, w = 0.2)) +
  labs(title = "Price over Time", 
       subtitle = "1 random product, 10 random stores",
       caption = "Each line represents and outlet through time") +
  facet_wrap(~`Primary GroupDesc`) +
  theme(legend.position = "none")

```

## Is price a predictor for Ordered Quantity?

This part will likely be wrong until I get those outliers above figured out, but wanted to get the code built anyway. 

```{r netvalue.modelling, echo=FALSE}

order.info %>%
  filter(NetPrice > 0) %>% 
  ggplot(aes(x = NetPrice, y = max.qty, color = as.factor(`Primary GroupDesc`))) +
  geom_jitter() +
  ggtitle("Price over Time", "1 random product, 10 random stores")

hist((order.info$max.qty), breaks = 35)

```